sdmTMB: an R package for fast, flexible, and user-friendly generalized linear mixed effects models with spatial and spatiotemporal random fields

### 2023-09-12 doc/paper-jss/paper-jss.Rmd
More description

and TODO

>>>>

where $\boldsymbol{\beta}$ are coefficients associated with the main effects, $O_{\boldsymbol{s},t}$ represents the offset (here, log area swept), $\gamma_t$ represents the time-varying coefficients, $\omega_{\boldsymbol{s}}$ is the spatial field (equivalent to a spatial intercept) and $\epsilon_{\boldsymbol{s},t} $ represents spatiotemporal fields.

The temporally varying intercepts $\gamma_t$ are modeled as a stationary AR(1) process,
